Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-04 journal paper/content/sec-model.tex
Small edits.

\xhdr{Extensions.} \asedit{The \TheoryModel admits several extensions, detailed in Section~\ref{sec:theory-extensions}. First, all/most results extend to arbitrary reward distributions, allow reward-dependent utility, and carry over to a more general version of multi-armed bandits. Second, agents could have beliefs on $(\alg[1],\alg[2],\priorMu,\respF)$ that need not be correct; then, all results carry over with respect to these beliefs. Third, all results carry over \asmargincomment{check}  if each agent $t$ has a prior on her arrival time $t$, rather than know it exactly. Fourth, we can handle a limited amount of non-stationarity in $\respF$. \asmargincomment{check} Finally, the main result on \HardMax extends to time-discounted utilities.
}

@@

\asedit{Principals' utilities are not discounted with time.%
\footnote{However, our main theoretical result on the greedy algorithm extends to time-discounted rewards.}
 While much of the early work on bandits focuses on  time-discounted rewards \citep{Gittins-book11}, non-discounted  formulations are prevalent in the bandits literature over the past two decades \citep{slivkins-MABbook,LS19bandit-book}, and better correspond to practical deployments \citep[\eg][]{DS-arxiv}. The distinctions between better and worse bandit algorithms are not as well-understood under time-discounting.}

>>>>

\xhdr{Extensions.} \asedit{The \TheoryModel admits several extensions, detailed in Section~\ref{sec:theory-extensions}. First, all/most results extend to arbitrary reward distributions, allow reward-dependent utility, and carry over to a more general version of multi-armed bandits. Second, agents could have beliefs on $(\alg[1],\alg[2],\priorMu,\respF)$ that need not be correct; then, all results carry over with respect to these beliefs. 
%Third, all results carry over \asmargincomment{check}  if each agent $t$ has a prior on her arrival time $t$, rather than know it exactly.
Third, we can handle a limited amount of non-stationarity in $\respF$. \asmargincomment{check} Finally, the main result on \HardMax extends to time-discounted utilities.
}

@@

\asedit{Bandit rewards are not discounted with time, reflecting the fact that non-discounted, regret-minimizing formulations has been prevalent in the bandits literature over the past two decades \citep{slivkins-MABbook,LS19bandit-book}, and better correspond to practical deployments \citep[\eg][]{DS-arxiv}. Also, the distinctions between better and worse bandit algorithms are not as well-understood under time-discounting.}
